---
title: "Major League Baseball Stadiums and Championships"
author: "Billy Caughey"
date: "April 28, 2018"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = F, warning = F)
library(tidyr)
library(dplyr)
```

## Introduction and Purpose

- A while ago, my friends and I were discussing where Major League Baseball (MLB) stadiums are.
- Additionally, we wanted to know which division in the MLB had the most world series wins.
- To this end, an app was created to answer these questions. The app will show were stadiums are and the number of championships by division.
- The app created is [here](https://williamcaugheyapps.shinyapps.io/worldseriescounts/)

## Data

- The data for this project was collected from various sources including MLB.com, and the zipcode database.
- Using the head() function, we can take a look at the data.

```{r looking at the data}
mlb <- read.csv("C:/Users/Owner/Dropbox (Personal)/Coursera/Developing Data Products/Week 4/worldSeriesCounts/baseball data.csv") %>%
    select("Team","Location","Latitude","Longitude","Championships")
head(mlb)
```

## Highest Championships

- When all divisions are selected, the AL East division has the most world series wins.

```{r graphics}

knitr::include_graphics("C:/Users/Owner/Dropbox (Personal)/Coursera/Developing Data Products/Week 4/worldSeriesCounts/Capture.PNG")

```

## Team density

- Based on the previous map, most of the teams are located in the northeastern United States.
- The team with the most championships is the New York Yankees (which makes me sad as a Toronto Blue Jays fan!)
